\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-04 doc/sw-system.tex
Closed #78, performance discussion subsection  now complete (#44)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
\caption{Stage 2 agent properties, separating veterans from stage 1 from new
volunteers. Point size represents total information generated, dashed lines
are drawn at the mean values for each sample.}
\label{fig:discuss:performance:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

However, most identification failures (around 60\%) seem to be due to the
random walk problem. While improved training will help reduce this effect, it
is here that targeted task assignment could help improve system performance.
We advertised stage 2 of the current project to all registered users; it was
taken up by stage 1 veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since stage 2 was quite short): of the 1964 volunteers who took part in
the stage 2 classification round, only 774 were veterans from stage 1.
\Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
on to stage 2 skill and contribution...

\todo{Phil}{Remake figure to show stage 2 skill vs stage 1 skill with point
size given by stage 2 contribution. Stage 2 newbies will need to be plotted to
have (0 +/- small) stage 1 skill, to show up as a cloud.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/stage2_veteran_contribution.png}
\caption{Stage 2 classifier skill, as a function of their stage 1 skill.
Veterans from stage 1  are shown in blue, while new volunteers are shown in
orange. Point size is proportional to the number of stage 2 classifications
made, while dashed lines are drawn at the mean values for each sample.
Restricting stage 2 to classifiers with high stage 1 skill could reduce the
noise in the system.}
\label{fig:discuss:performance:stage1vstage2}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

However, most identification failures (around 60\%) seem to be due to the
random walk problem. While improved training will help reduce this effect, it
is here that targeted task assignment could help improve system performance.
We advertised stage 2 of the current project to all registered users; it was
taken up by stage 1 veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since stage 2 was quite short): of the 1964 volunteers who took part in
the stage 2 classification round, only 774 were veterans from stage 1.
\Fref{fig:discuss:performance:stage1vstage2} shows how the stage 1 skill maps
on to stage 2 skill and contribution.
